---
Title: "Lab 4"
Name: Tyler Edvall
Date: 02/11/21
output: github_document
---

1. Print a table containing only species NOT in the Order Passeriformes. Include all columns.

```{r}

# Bird orders data ------------------------------------------------------

#Load packages----

library(tidyverse)
library(auk)                          # load the auk package

#Read data----

birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa

birds

#Table 1

nopassbirds <- filter(birds, order != "Passeriformes")
nopassbirds

```

2. Print a table containing only species in the Order Passeriformes. Include all columns.

```{r}

#Table 2

passbirds <- filter(birds, order == "Passeriformes")
passbirds

```

3. Print a table containing all species. Only the variables Species Code, Scientific Name, and Common Name should be in the final table.

```{r}

#Table 3 

T3 <- select(birds, species_code, scientific_name, common_name)
T3

```

4. Print a table with all species in the Order Passeriformes whose common name starts with the word “Common”. Species should be in reverse taxonomic order (taxon_order variable). Only the variables Species Code, Scientific Name, and Common Name should be in the final table.

```{r}

#Table 4

passbirds <- filter(birds, order == "Passeriformes")
passbirds
T4 <- select(passbirds, species_code, scientific_name, common_name)
filter(T4, str_detect(common_name, "Common"))

```

5. Print a table containing species with “Warbler” in the common name. Include all columns.

```{r}

#Table 5

T5 <- filter(birds, str_detect(common_name, "Warbler"))
T5

```

6. Print a table with two columns; family and n, the number of species in that family whose name contains “Warbler”

```{r}

T6 <- count(birds, "Warbler")
T6

```

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```
